\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0cm}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------
% Custom Commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{2pt}}
  }
}

\newcommand{\resumeSubHeading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------------------------------

\begin{document}

%------HEADING---------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Jacob Grunwald} & Email : \href{mailto:jacob.grunwald@colorado.edu}{jacob.grunwald@colorado.edu}\\
  \href{https://github.com/jgrun}{https://github.com/jgrun} & Mobile : 832-585-4297\\
\end{tabular*}

%---------EDUCATION---------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubHeading
      {University of Colorado, Boulder}{Boulder, CO}
      {Bachelor of Science in Electrical and Computer Engineering;  GPA: 3.194}{Aug. 2014 -- May 2018}
  \resumeSubHeadingListEnd

%----------EXPERIENCE--------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubHeading
      {Halleck Willard Inc.}{Frederick, CO}
      {Embedded Systems Engineering Intern}{May 2017 - Aug. 2017}
      \resumeItemListStart
        \resumeItem{Eggbot}
          {Ported code for the Eggbot from Evil Mad Scientists to a Renesas S1 ARM cortex microprocessor. Modified code to take advantage of multithreading and an RTOS.}
        \resumeItem{PCB Design}
          {Designed a microcontroller to mimic the hardware of the Eggbot using Altium. Designed a connector shield for a Renesas development board with Altium.}
        \resumeItem{Module Guides}
          {Helped to test and verify Renesas Synergy Module Guides. Ran test code and proofread module documentation.}
      \resumeItemListEnd

    \resumeSubHeading
      {Colorado Space Grant Consortium RocketSat11}{Boulder, CO}
      {Avionics Team Member}{Sep. 2016 - May 2017}
      \resumeItemListStart
        \resumeItem{Software}
          {Designed and tested software to integrate several sensors and cameras into a sounding rocket payload while maximizing sampling frequency}
        \resumeItem{Hardware}
          {Assisted in design and testing of hardware components for a sounding rocket payload. Focused particularly on testing communication protocols and integration of sensors with same communication protocols.}
      \resumeItemListEnd

    \resumeSubHeading
    {Electrical, Computer, and Energy Engineering Department}{Boulder, CO}
    {Course Assistant}{Sep. 2015 - Dec. 2016}
    \resumeItemListStart
      \resumeItem{CU Arduino}
        {Designed and built an Arduino platform for use in the departments freshman projects course.}
      \resumeItem{Student Help}
        {Assisted students in class work for ECEN 1400, a freshman electrical engineering projects class. Work included helping students to understand electrical engineering and programming concepts.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Programming}{: C, some Assembly, Verilog}
      \hfill
      \textbf{CAD}{: Quartus Design, Altium Design}
      \hfill
      \textbf{OS}{: Windows, Linux}
    }
  \resumeSubHeadingListEnd

%----------LEADERSHIP---------
\section{Leadership}
  \resumeSubHeadingListStart
    \resumeSubItem{President of the Electrical Engineering Student Society}
      {Organized and led social, technical, and networking events for the Electrical, Computer, and Energy Engineering Department at CU Boulder}
    \resumeSubItem{Fundraising}
      {Led a team of 9 students in raising \$8,000 for LIMBS International, a non-profit group dedicated to donating artificial legs to those in need, over the course of six months.}
    \resumeSubItem{Teamwork}
      {Worked with a group of 12 others to create and run pre-teen oriented programs at South Regional Library of the Montgomery County Library System for four years.}
  \resumeSubHeadingListEnd
\end{document}
