%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{
University Corporation for Atmospheric Research \\
P.O. Box 3000 \\
Boulder, CO 80307}

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Jacob Grunwald \\ jacob.grunwald@colorado.edu \\
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
2311 Walnut St. Apt. 4 \\ Boulder, CO 80302 \\ (832) 585-4297 % Your address and phone number
\end{center}
\vfill

%\signature{Jacob Grunwald} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{To whom it may concern,}

I am writing to apply for the high performance computing futures lab student assistant position posted on your website.

I am currently a senior at CU Boulder and will be graduating with a BS in electrical and comuputer engineering with a minor in computer science May of 2018. I found out about the open position while looking through CU Career Services open listings. I am interested in the HPCFL position because I am highly interested in computer and network systems. This is a newer interest of mine, starting with my senior capstone project where we are creating an ad-hoc network for communication between vehicles. In this project I am in charge of generating the network and I have been finding the work very interesting. For the project, I have had to teach myself how to write and debug TCP sockets as well as unix domain sockets and have been working on integrating a custom built PCB with the OBD-II system of my vehicle. Based on my experience so far, I want to learn more about systems administration and feel that UCAR can help me with this.

If you find me qualified, I would love to meet in person. I tend to be most responsive to email, so please email me at jacob.grunwald@colorado.edu. Alternatively, call me at (832) 585-4297. Thank you for your time and consideration and I hope to hear from you soon!

%\closing{Sincerely yours,}
Sincerely yours,

Jacob Grunwald

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
