%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Ms. Taapken \\
Phase IV Engineering Inc. \\
2820 Wilderness Place Unit C \\
Boulder, CO 80301}

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Jacob Grunwald \\ jacob.grunwald@colorado.edu \\
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
2311 Walnut St. Apt. 4 \\ Boulder, CO 80302 \\ (832) 585-4297 % Your address and phone number
\end{center}
\vfill

%\signature{Jacob Grunwald} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Ms. Taapken,}

I am writing to apply for the firmware engineering position posted on your website.

I am currently a senior at CU Boulder and will be graduating with a BS in electrical and comuputer engineering with a minor in computer science May of 2018. I came across Phase IV while looking for companies involved in embedded systems in Boulder. Programming, designing, and debugging embedded systems has been a focus in my education since I was first introduced to them my sophomore year here. I got a taste of what it was like to work in the industry while working at Halleck Willard Inc. over the past summer, but am now looking to expand upon that experience with Phase IV. Since then, I have been helping to design a system for use in vehicles that communicates information like velocity, acceleration, signal indicator status, and heading to nearby vehicles for my senior design project. In doing so, I have had to teach myself how to write and debug TCP sockets as well as unix domain sockets and have been working on integrating a custom built PCB with the OBD-II system of my vehicle. I have greatly enjoyed working on this and feel, based on what I have learned about Phase IV, that your company offers the next step in this journey.

If you find me qualified, I would love to meet at Phase IV in person. I tend to be most responsive to email, so please email me at jacob.grunwald@colorado.edu. Altrenatively, call me at (832) 585-4297. Thank you for your time and consideration and I hope to hear from you soon!

%\closing{Sincerely yours,}
Sincerely yours,

Jacob Grunwald

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
